Supplementary material

### 2019-02-28 Manuscript/ms.tex
Adding author summary

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
% \section*{Author summary}

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

The contribution of the mosquito vector \emph{Aedes aegypti} to the spread of dengue fever depends not only on their abundance, but also on the likelihood of an exposed mosquito living long enough to incubate the dengue virus and subsequently it transmit to a susceptible human host.
We developed a mechanistic model that accounts for the role of this process in the dynamics of dengue fever and fit the model to a time series of human case reports and mosquito trap counts from the city of Vitoria, Brazil.
We then used this fitted model to simulate the effect of mosquito control implemented at different times of the year and found that  mosquito control leads to the largest reduction in human dengue cases during a given year when applied at the local minimum of the previous year’s human immunity trajectory.
Further, the effectiveness of mosquito control was strongly correlated with how quickly previously infected humans become susceptible again, with mosquito control making the largest impact when immunity wanes quickly.
Thus, the effects of mosquito control efforts are tightly coupled with the dynamics of human immunity and the long-term lags and feedbacks generated by the epidemiological system.
